Bayesian statistics and swine flu

### 2009-09-25 docs/pandemic/bayesPandemic.rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@414 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\column{0.5\textwidth}
\begin{block}{Hospitalization}
<<probS>>=
plot(params$age$S, type="l", ylim=c(0,0.06))
@
\end{block}

\column{0.5\textwidth}
\begin{block}{Death}
<<probD>>=
plot(params$age$D, type="l", ylim=c(0,0.06))
@

@@

\begin{frame}
\frametitle{Posterior and prior, Hosp $\Rightarrow$ Death }
<<priorPost, fig=false,results=tex>>=
library(ellipse)
plotPrior(priors, paramSample, transition="MedHospS",file="MedHospS", tex=TRUE)
@
\end{frame}

@@

\begin{frame}[fragile]
\frametitle{Hospital demand}
<<hospLoad,echo=T>>=
# generate hospital times
hospSample = simHospitals(paramSample , Ndays=60, 
	NinfectionsPerDay=c(seq(10, 100, len=30),seq(100, 10, len=30) ) )

@@

\begin{frame}[fragile]
\frametitle{With rising and falling incidence}
{\scrpitsize
<<hospLoad2,echo=T,height=2,width=4>>=
# generate hospital times
hospSample2 = simHospitals(paramSample , Ndays=40, 
	NinfectionsPerDay=c(seq(from=1,by=2, len=10), seq(from=20, len=10, by=2), rep(2, 20)))

>>>>

\column{0.5\textwidth}
\begin{block}{Hospitalization}
<<probS>>=
plot(params$age$S, type="l", ylim=c(0,0.1))
@
\end{block}

\column{0.5\textwidth}
\begin{block}{Death}
<<probD>>=
plot(params$age$D, type="l", ylim=c(0,0.1))
@

@@

\begin{frame}
\frametitle{Posterior and prior, Med $\Rightarrow$ Hosp }
<<priorPost, fig=false,results=tex>>=
library(ellipse)
plotPrior(priors, paramSample, transition="MedHospS",file="MedHospS", tex=TRUE)
@
\end{frame}

@@

\begin{frame}[fragile]
\frametitle{Hospital demand}
<<hospLoad,echo=T>>=
# generate hospital times
hospSample = simHospitals(paramSample , Ndays=80, 
	NinfectionsPerDay=20 )

@@

\begin{frame}[fragile]
\frametitle{With rising and falling incidence}
{\scrpitsize
<<hospLoad2,echo=T,height=2,width=4>>=
# generate hospital times
hospSample2 = simHospitals(paramSample , Ndays=80, 
	NinfectionsPerDay=c(seq(1, 100, len=20),seq(100, 1, len=20), rep(2, 40) ) )
